% Entwurf der Doktorarbeit von Domenik Zimmermann, TU M\"unchen, Grp. Prof. Dr. Auw\"arter 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Domenik Matthias Zimmermann}
\title{Molecular functionalization of \textit{h}-BN}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bilder: AFM/STM 1024x1024 px exportieren, 
%
% Fonts are embedded by default, otherwise check 
% https://tex.stackexchange.com/questions/10391/how-to-embed-fonts-at-compile-time-with-pdflatex
% 
% sudo apt-get install kile texlive-latex-extra texlive-science texlive-bibtex-extra biber
% adjust kile tools to call biber %lS instead of bibtex
%
% If errors occure referring to aux files or others:
%	Delete helper files (*.aux) and maybe others!
%
% Use MikTeX version 2.9.6615 or later (check that biber is included)
% Using BiBLaTex, biber as frontend.
% If biber complains (ERROR - Error: Found biblatex control file version 2.6, expected version 3.4.)
% 	Update with your Miktex package manager (mpm_mfc.exe[single user install] or mpm_mfc_admin.exe [all user install])
% no new biblatex version there? Sync database? NO improvement!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Setup for document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[
10pt,					% Schriftgröße
a4paper,				% A4 paper
twoside,				% Zweiseitig
BCOR=8mm,				% Bindekorrektur inkl. Biegefalz
headings=normal,		% Kleinere Kapitelüberschriften => check preamble
headsepline,			% Enable line to seperate head ...
footsepline,			% ... and foot
plainfootsepline,		% Footseperation line on chapter start
%,draft
]{scrbook}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Change Page Geometry %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[
top=30mm,
bottom=55mm,
inner=25mm,
outer=30mm,
%marginparsep=7mm,
%marginparwidth=48mm,
%paperwidth=210mm,
%paperheight=245mm, 286mm (A4)
]{geometry}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{./includes/preamble}
\input{./includes/commands}
%%%%%%%%%%%%%%%%%%%% Draft Mode Compilation from command line %%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%% pdflatex "\def\draftmode{1} \input{FILE}"  %%%%%%%%%%%%%%%%%%
%%%%%% TEXSTUDIO %%% pdflatex "\def\draftmode{1} \input{%.tex}" %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\def\daumenkino{1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 \input{./includes/frontmatter/cover}											%					%
 \frontmatter{}			 														%					%
   \input{./includes/frontmatter/titlepage}										%					%
   \input{./includes/frontmatter/disclaimer}									% 					%
   \input{./includes/frontmatter/acknowledgements}								%	 				%
   \input{./includes/frontmatter/abstract}										%					%
 \microtypesetup{protrusion=false}												%					%
 \setcounter{tocdepth}{4}														%   [1=sections]	%
	\tableofcontents{}														 	% 					%
% 	\listoffigures														 		% 					%
% 	\listoftables																% 					%
 \microtypesetup{protrusion=true}												%		 			%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{./includes/frontmatter/preface}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mainmatter{}
\chapter{Introduction}
\input{./includes/chapter/introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Experimental methods}
Several experimental methods are used within this work to determine different physical properties. In this chapter we review the principles, benefits and limitations for each method. All of them are well known in surface science and used to analyze thin films on different substrates with respect to their geometric, electronic and chemical properties.

  \section{\textbf{S}canning \textbf{T}unneling \textbf{M}icroscopy}
    \input{./includes/chapter/stm-technique}
    \subsection{\textbf{S}canning \textbf{T}unneling \textbf{S}pectroscopy}
      \input{./includes/chapter/sts-technique}
  \section{\textbf{X}-ray \textbf{P}hotoelectron \textbf{S}pectroscopy}
	\input{./includes/chapter/xps-technique}
  \section{\textbf{A}tomic \textbf{F}orce \textbf{M}icroscopy}
	\input{./includes/chapter/afm-technique}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Experimental setup and sample preparation}
To conduct experiments in the most controlled environment possible, sample preparation is done in ultrahigh vacuum (UHV) chambers. With a base pressure of $\approx \SI{5e-10}{\milli \bar}$ these stainless steel chambers are almost free of contaminants. After cleaning the metallic substrates, ad-layers and molecular species are deposited and investigated. Experiments were done at different experimental chambers: (1) A LT-STM chamber. The technical aspects of the preparation and experimental chamber are discussed elsewhere \cite{urgel_tendero_two-dimensional_2015, schwarz_assembly_2018, wiengarten_scanning_2015} and shortly summarized here. (2) A RT-STM with XPS capabilities. The technical aspects and build details are given in \cite{schwarz_assembly_2018}. (3) The NIM-XPS chamber. 
%This chamber is chosen because of it is possible to investigate chemical properties and coverage with XPS while an UV-Vis spectrometer is used to access the electronic structure of the occupied states. 
(4) A LT-AFM machine offers a complementary investigation method for geometric information. Its setup details can be found in \cite{he_bottom-up_2017}.


  \section{Experimental setup}
    \input{./includes/chapter/experimental-setup}
  \section{Substrates and ad-layers}
Molecular adsorption experiments are done with single crystalline substrates of copper and silver, terminated at (111) and (100) surfaces. Polycrystalline copper foils and gold evaporated on mica are used as well. Some experiments are done to investigate molecules on \textit{h}-BN/Cu(111) and \textit{h}-BN/Cu(foil). 

The following sections will describe the relevant physical properties of the various substrates and will introduce a method to prepare polycrystalline copper foils to grow \textit{h}-BN on. An example for chemical vapor deposition of borazine on a transition metal surface is given. The geometric properties of the resulting lattice mismatched system are discussed briefly. The molecules used for experiments are introduced at the end of the chapter.
     \subsection{Single crystal substrates}
        \input{./includes/chapter/crystal}
  %   \subsection{Surface states}
	%	\input{./includes/chapter/surface-states}
     \subsection{Polycrystalline substrates}
     As was mentioned before, clean, highly ordered surfaces are desirable to perform experiments on. Effort is done to clean the surfaces before every experiment to ensure a reproducible environment and interpretable results. This lead to a detailed understanding of the physics and chemistry behind a lot of systems. In case a systems order and functionality does not heavily depend on the substrates symmetry, single crystals loose most of their unique selling point. Instead of choosing a expensive bulk single crystal, thin copper foils can catch up in production environments. The mass produced foils still show some inconvenient properties. Although pure copper foils ($\geq \SI{99.999}{\percent}$) are available, their surface was never meant to be atomically flat. 
     A representation of a copper surface before electro polishing can be seen in figure \ref{fig:copper-foil-grains}. Here the layered structure of the (mechanically polished) foil is apparent and shows different sizes of grains and annealing twins at the surface. Small subgrains constitute the uppermost layers, while deeper lying layers consist of larger grains with grain boundaries becoming more and more diffuse with increasing distance to the surface.
     
     The surface termination is not homogeneous and is made of several domains with different facet orientation thus showing different step heights as indicated in table \ref{tab:step-heights}.
     \subsubsection{Electropolishing}
    	\input{./includes/chapter/electropolishing}
     \subsection{Growing atomically thin ad layers with \textbf{C}hemical \textbf{V}apor \textbf{D}eposition}
        \input{./includes/chapter/cvd}
\clearpage             
     \subsection{Geometric effects in ad-layers}
		\input{./includes/chapter/moire}
  \section{Used molecules}
    \input{./includes/chapter/used-molecules}
%\printbibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\chapter{Pyrene}
%\section{on h-BN on Cu(111)}
%\input{./includes/chapter/pyrene-paper}
%%\printbibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\chapter{Helicene}
%\section{on Ag(100) and (111)}
%\section{on h-BN on Cu(111)}
%\input{./includes/chapter/helicene-paper}
%%\printbibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Epitaxial hexagonal boron nitride on copper foils}
  \input{./includes/chapter/motivation-copper-foils}
\section{Pre-treatment of Cu-foils: Polishing}
  	\input{./includes/chapter/etching-experiment}
  \section{Characterization: SEM \& STM of \textit{h}-BN on Cu-foil}
     \input{./includes/chapter/bn-on-foil}
  \section{Characterization: XPS of self-grown \textit{h}-BN/Cu-foils}
     \input{./includes/chapter/xps-self-grown-foils}
  \section{Characterization: XPS of bought \textit{h}-BN/Cu-foils}
     \input{./includes/chapter/xps-as-bought}
  \section{Application: Molecular functionalization with TPCN}
     \input{./includes/chapter/TPCN-on-h-BN-on-Cu-foil}
  \section{Conclusion}
     \input{./includes/chapter/foils-conclusion}
%\printbibliography	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\chapter{TPCN}
%%  \section{on Cu(111)}
%%    \input{./includes/chapter/TPCN-on-Cu111}
%%   \section{on h-BN on Cu(111)}
%%    \input{./includes/chapter/TPCN-on-h-BN-on-Cu111}
%%\printbibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Tert-Butyl-Phenyl Porphine}
    \input{./includes/chapter/TBP-intro}
  \section{Single leg functionalization}
   \subsection{on Cu(111)}
      \input{./includes/chapter/TBP-on-Cu111}
   \subsection{on Ag(100)}
      \input{./includes/chapter/TBP-on-Ag100}
   \subsection{on \textit{h}-BN}
      \input{./includes/chapter/TBP-on-h-BN}
%\printbibliography
	\subsection{Conclusion}
      \input{./includes/chapter/TBP-conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \section{Double leg functionalization}
   \subsection{on Cu(111)}
      \input{./includes/chapter/TBP-double-Cu111}
   \subsection{on Ag(100)}
      \input{./includes/chapter/TBP-double-Ag100}
%\printbibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Borazine functionalized coronene}
Coronene ($C_{24}H_{12}$, known as [6]circulene or superbenzene) is a polycyclic aromatic hydrocarbon made of six carbon rings to form a molecule reminiscent of a small graphene flake. It belongs to the family of circulenes where a central polygon is enclosed by different numbers of fused benzenoids. For example [5]circulene (corannulene), [6]circulene (coronene), [7]circulene,[2][3][4][5] and higher orders could be synthesized and show different conformation. While species with [5] or [7] benzene rings are bowl shaped, coronene is flat.

	\section{Find a nice title!}
		\input{./includes/chapter/HBC-HBBNC}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Summary}
      \input{./includes/chapter/summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\backmatter{}
  \printbibliography  
\chapter{Appendix}
%\addcontentsline{toc}{chapter}{Index}
%  \addcontentsline{toc}{chapter}{Appendix}
%  \input{./includes/backmatter/backmatter}
\section{Crystal facets}
  \input{./includes/chapter/backmatter/crystal-facet}
    %% Orbital calculations
\section{Orbital calculations for pyrene molecules}
In this section extended hückel theory calculations of functionalized pyrene molecules are shown. After structural relaxation via the AM1 semi-empirical method in the Hyperchem software, the result is exported to an IGOR script for presentation. Single molecular orbitals as well as their sum can be shown. For all molecules some basic information is given in a box. The number of atoms, electrons and calculated orbitals is given together with a ball and stick model of the corresponding molecule. Calculated HOMO/LUMO states are shown to the right with their energies noted below.
The left side of the pages shows occupied states (second column) and their sum (first column). The right side shows the unoccupied in the same manner.

The first two pages will show cis-pyrene as calculated in gas phase together with a model showing the rotation of pyridil legs and the influence on molecular orbitals. Trans- \& tetra-pyrene molecules are shown afterwards.

Due to the same molecular center, all the species show distinct symmetry at their pyrene center. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Change to larger page layout
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newgeometry{top=2cm,bottom=2cm}%
%
  \input{./includes/chapter/backmatter/EHT-cis-pyrene}
  \input{./includes/chapter/backmatter/EHT-cis-pyrene-60}
  \input{./includes/chapter/backmatter/EHT-trans-pyrene}
  \input{./includes/chapter/backmatter/EHT-tetra-pyrene}
\restoregeometry
  \input{./includes/chapter/backmatter/TBP-distance}
\begin{landscape}
\section{Python interface for a Maxigauge-TPG256A}
  \pythonexternal{./includes/chapter/backmatter/Maxigauge-TPG256A.py} %see commands for this 
\end{landscape}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Restore page layout
\restoregeometry
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     %% TBP-Appendix
 \section{Ordered areas of TBP}
 \input{./includes/chapter/backmatter/Appendix-tbp}
 %%%%%%%%%%%%%%%%%%%%
%% HBBNC-Appendix
\section{HBBNC}
\input{./includes/chapter/backmatter/HBBNC-SI} 
\end{document}