\addcontentsline{toc}{chapter}{Acknowledgments}		%Entry in TOC
\thispagestyle{empty}
%\vspace*{2cm}
\begin{center}
{\usekomafont{section} Acknowledgments}
\end{center}
\vspace{1cm}
A lot of people are invoked in the course of the thesis and I like to thank them for their support. First and foremost I like to thank Prof.\ Dr.\ W.\ Auw\"arter for the opportunity to work in his research group. The wide field of molecular assembly and functionalization opened up many interesting insights that would never be possible without him. The time dedicated to experiments under his leadership was very exciting and his review challenged my ambition to further improve. Together with Prof.\ Dr.\ J.\ Barth a very pleasant professional environment was created with retreats and group activities framing our day-to-day work.

Besides them, many people were incorporated at different levels, starting from introducing technical aspects and measurement techniques used at the different setups via result discussion through to proof-reading and concept validation. 

	Dr.\ A.\ Wiengarten was the operator of the low temperature scanning tunneling microscope and I started under her supervision with the first measurements. Her profound understanding of the setup shared with me was consolidated by Dr.\ K.\ Seufert whose deep commitment nurtured my engagement. His enjoyment of work eased many hours in the lab.

	Measurements at the low temperature atomic force microscope are supported by M.\ P\"ortner and S.\ Synkule. Their fruitful result discussion together with Dr.\ A.\ Riss clarified topics in technical and scientific aspects easily.

	The combined room temperature STM and X-Ray photoelectron spectroscopy setup was assembled by Dr.\ M.\ Schwarz whose continuous efforts in setup details enabled the use of this machine. Together with discussion and operational help of A.\ Baklanov, many measurements were done smoothly.

	Further XPS measurements were done at the machine operated by the Nanosystems Initiative Munich represented by \textbf{\underline{LALALA}} and advocated by Dr.\ J.\ Reichert. Scientific discussion with him, K.\ Eberle and Prof.\ Dr.\ Feulner often lead to meaningful outcomes and was always a pleasure.

	The few measurements at the scanning electron microscope were done under supervision of Dr.\ \textbf{\underline{LALALA}} and Y.\ Gong.

	Please let me thank all member of E20 for a nice time together that showed me the value of social interaction combined with consuming delights and limits.

\begin{center}Thank you.
\newpage 
\thispagestyle{empty}
Dedicated to the beloved ones that made me who I am. Without you these endless lines of text would never end. 
%\epigraph{All work and no play makes Jack a dull boy}{James Howell\\Paroimiographia}
%\epigraph{Goodbye, Jake. I love you, dear.}{Stephen King, The Dark Tower} 
\epigraph{Gone. Like a candle-flame. To whatever worlds there are.}{Stephen King, The Dark Tower}
\epigraph{We go to seek a better world. May you find one, as well.}{Stephen King, The Dark Tower}
\end{center}
\cleardoublepage{}